Contextual Combinatorial Cascading Bandits

### 2015-12-22 experiment.tex
update readme
fixed conj/disj;

\usepackage{fullpage}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{courier}
\usepackage{tikz}

@@

This section introduced Movielens dataset and its movie recommendation challenge. Let $L=\#\text{movies}$, Movielens is a matrix $A\in \{0,1\}^{\#\text{users}\cdot L}$ where each entry $A_{ij}$ is a boolean clickthrough indicator for the $i$-th user and the $j$-th movie. We split $A=A^1+A^2$, by randomly putting hot entries in $A$ into $A^1$ and $A^2$ accoring to a bernulli distribution. At round $t$, a user indexed $i_t$ is randomly selected from a predefined set of users, and the agent is required to recommend movies using $A^1$ and $\mathcal{H}_t$ such that $A^2_{i_tj}=1$ for as many those recommended $j$s as possible.

@@

\end{enumerate}
\end{document}

>>>>

\usepackage{fullpage}
\usepackage{courier}
\usepackage{tikz}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{amsmath, amssymb, amsfonts, bm}
\usepackage{algorithm,algorithmic}
\usepackage{amsthm}
\usepackage{float}
\usepackage{graphicx}
\usepackage{booktabs}

@@

This section introduced Movielens dataset and its movie recommendation challenge. Let $L=\#\text{movies}$, Movielens is a matrix $A\in \{0,1\}^{\#\text{users}\cdot L}$ where each entry $A_{ij}$ is a boolean clickthrough indicator for the $i$-th user and the $j$-th movie. We split $A=A^1+A^2$, by randomly putting hot entries in $A$ into $A^1$ and $A^2$ according to a bernulli distribution. At round $t$, a user indexed $i_t$ is randomly selected from a predefined set of users, and the agent is required to recommend movies using $A^1$ and $\mathcal{H}_t$ such that $A^2_{i_tj}=1$ for as many those recommended $j$s as possible.

@@

An example output, with $T=10000$, is listed below.

\begin{table}
    \centering
    \renewcommand{\arraystretch}{1.2}
	\begin{tabular}{lc}
	    \toprule
		\textbf{Algorithm}  &\textbf{Cumulative Reward $\sum_{t=1}^Tr_i $}\\
		\midrule
		Li		    &4342.73 \\
		Qin		    &4323.26 \\
		Monkey		    &1765.41 \\
		Kveton		    &1787.81 \\
		Perfect Play		    &N/A \\
		\bottomrule
	\end{tabular}
	\caption{\textbf{Cumulative reward w.r.t different baselines, under Movielens setting.}}
	\label{daily}
\end{table}
\end{document}
